Treebeard : An Optimizing Compiler for Tree Based ML Inference

### 2022-04-15 docs/MICRO 2022/tiling.tex
Add interleaving, vectorization, parallelization
Add new tiling diagrams

\subsection{Tiling}

Treebeard vectorizes tree walks by grouping nodes of a decision tree into \textbf{\emph{tiles}}. The nodes in a tile are evaluated concurrently using vector instructions. Once the nodes of the current tile are evaluated, a look up table is used to compute which child of the current tile to move to next. The listing below shows at a high level how a tiled tree is walked. 
\begin{lstlisting}[style=c++]
  // A lookup table that determines the child index of
  // the next tile given the tile shape and the outcome
  // of the vector comparison on the current tile
  int16_t LUT[NUM_TILE_SHAPES, pow(2, TileSize)]

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/TileShapes_Size3.PNG}
  \caption{All possible tile shapes with a tile size $n_t=3$}
  \label{Fig:TileSize3Shapes}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/TiledTree_Size3.PNG}
  \caption{Example of a valid tree tiling with a tile size $n_t=3$}
  \label{Fig:ValidTilingTileSize3}
\end{figure}

>>>>

\subsection{Tiling}
\label{sec:Tiling}
Treebeard vectorizes tree walks by grouping nodes of a decision tree into \textbf{\emph{tiles}}. The nodes in a tile are evaluated concurrently using vector instructions. Once the nodes of the current tile are evaluated, a look up table is used to compute which child of the current tile to move to next. The listing below shows at a high level how a tiled tree is walked. 
\begin{lstlisting}[style=c++]
  // A lookup table that determines the child index of
  // the next tile given the tile shape and the outcome
  // of the vector comparison on the current tile
  int16_t LUT[NUM_TILE_SHAPES, pow(2, TileSize)]

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/TileShapes_Size3.PNG}
  \caption{All possible tile shapes with tile size $n_t=3$}
  \label{Fig:TileSize3Shapes}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/TiledTree_Size3.PNG}
  \caption{Example of a valid tree tiling with tile size $n_t=3$}
  \label{Fig:ValidTilingTileSize3}
\end{figure}
